Robust and Efficient CSI Compression Using CLLWCsiNet in Noisy MIMO Environments

### 2025-04-07 paper_latex_edit - Copy.tex
for second time i revised the formulas in system model , since the SNR in calculations is related to NMSE ( error )

\documentclass[lettersize,journal]{IEEEtran}
\usepackage{amsmath,amsfonts}
\usepackage{algorithmic}
\usepackage{array}
\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\usepackage{textcomp}
\usepackage{booktabs}
\usepackage{stfloats}
\usepackage{url}
\usepackage{booktabs,multirow, threeparttable}
\usepackage{multicol}
\usepackage{lipsum}% http://ctan.org/pkg/lipsum
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
%\usepackage{subfigure}
%\usepackage{subfig}
\hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\usepackage{balance}
\begin{document}
\title{Robust and Efficient CSI Compression Using CLLWCsiNet in Noisy MIMO Environments}

@@

>>>>

\documentclass[lettersize,journal]{IEEEtran}
\usepackage{amsmath,amsfonts}
\usepackage{algorithmic}
\usepackage{array}
\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\usepackage{textcomp}
\usepackage{booktabs}
\usepackage{mathtools}
\usepackage{stfloats}
\usepackage{url}
\usepackage{booktabs,multirow, threeparttable}
\usepackage{multicol}
\usepackage{lipsum}% http://ctan.org/pkg/lipsum
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
%\usepackage{subfigure}
%\usepackage{subfig}
\hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\usepackage{balance}
\begin{document}
\title{Robust and Efficient CSI Compression Using CLLWCsiNet in Noisy MIMO Environments}

@@

\subsection{End-to-End Effective SNR Analysis}
The effective SNR at the receiver accounts for both channel estimation and compression errors. Let $\mathbf{H} \in \mathbb{C}^{N_c \times N_t}$ denote the true channel matrix, and $\hat{\mathbf{H}} = \mathbf{H} + \mathbf{E}_{\text{est}}$ its estimate from pilot symbols, where $\mathbf{E}_{\text{est}}$ is the estimation error matrix with i.i.d. elements $\sim \mathcal{CN}(0,\sigma_{\text{est}}^2)$. After compression/decompression, the reconstructed channel becomes:

\begin{equation}
\hat{\tilde{\mathbf{H}}}_f = \tilde{\mathbf{H}}_f + \mathbf{E}_{\text{comp}}, \quad \mathbf{E}_{\text{comp}} \sim \mathcal{CN}(0,\sigma_{\text{comp}}^2)
\end{equation}

The \textbf{effective SNR} for data detection is derived as:

\begin{equation}
\text{SNR}_{\text{eff}} \coloneqq \frac{\mathbb{E}\{\|\mathbf{H}\|_F^2\}}{\mathbb{E}\{\|\mathbf{E}_{\text{total}}\|_F^2\}} = \frac{N_t N_c P}{\sigma_{\text{est}}^2 + \sigma_{\text{comp}}^2 + N_0}
\end{equation}

\noindent where:
\begin{itemize}
\item $P$ is the transmit power per subcarrier
\item $\sigma_{\text{est}}^2 = \frac{N_0}{T_p E_p}$ is the pilot-based estimation error variance ($T_p$: pilot length, $E_p$: pilot energy)
\item $\sigma_{\text{comp}}^2 = \|\mathbf{F}_a\|^2 \cdot 10^{\text{NMSE}/10} \cdot P$ converts NMSE to compression error power
\item $N_0$ is the thermal noise density
\end{itemize}

For orthogonal pilots with $T_p \geq N_t$, this simplifies to:

\begin{equation}
\text{SNR}_{\text{eff}} = \frac{N_t \gamma}{1 + \gamma\left(\frac{1}{\beta} + 10^{\text{NMSE}/10}\right)}, \quad \text{where } \gamma \coloneqq \frac{P}{N_0}
\end{equation}

\noindent and $\beta \coloneqq T_p E_p/N_0$ is the pilot SNR.
